\justify

\hspace{2em} The Higgs boson was proposed in the 1960s as one of the fundamental particles in the Standard Model (SM) of particle physics,
In 2012, the ATLAS and CMS experiments at the LHC discovered a scalar boson with a mass about 125 GeV 
that was later confirmed, through dedicated measurements of its properties, to be the Higgs boson of the SM.
The Higgs boson couplings strengths to other SM bosons and fermions are essential parameters to the SM theory,
and the measurements of them have become a focus of the LHC physics programs.
The study of the Higgs to muons decay is of particular importance 
as it is the most experimentally sensitive probe of the Higgs couplings to second-generation fermions at the LHC.

This thesis reports the first evidence for the Higgs boson decay to a pair of muons,
based on proton-proton collision data at $\sqrt{s}$ = 13 TeV recorded by the CMS experiment at the LHC, 
corresponding to an integrated luminosity of 137 $\text{fb}^{-1}$.
The analysis is performed in four exclusive categories targeting different production modes of the Higgs boson:
gluon fusion, vector boson fusion, associated production with a vector boson, and associated production with a top quark pair.
This thesis is focused on a novel muon momentum correction and the exclusive analysis of the Higgs boson production in association with a vector boson,
in which an excess of events over the background expectation is observed in data with a significance of 2.0 standard deviations,
while the expected significance for the SM Higgs boson with mass of 125.38 GeV is 0.42 standard deviations.

This thesis also presents the combined result of the four exclusive categories. 
The overall observed significance is 3.0 standard deviations, 
while the expectation for the SM Higgs boson with mass of 125.38 GeV is 2.5.
This result is also combined with the that from the data recorded at $\sqrt{s}$ = 7 and 8 TeV, 
corresponding to integrated luminosities of 5.1 and 19.7 $\text{fb}^{-1}$, respectively,
whose effect is an increase in both the expected and observed significance by 1\%.
The measured signal strength. relative to the SM prediction, is $1.19^{+0.40}_{-0.39} \text{(stat)}^{+0.15}_{-0.14} \text{(syst)}$.
This result establishes the first evidence for the Higgs boson decay to second generation fermions
and provides the most precise measurement of the Higgs boson coupling to muons to date.