%\justify

\hspace{2em} I am grateful to have had great mentors, colleagues, and friends during my Ph.D. study,
without whom I could not have completed this wonderful journey.

I would like to convey my gratitude to my advisor Prof. Darin Acosta,
who has been an excellent mentor and a true friend.
He has provided me guidance on many aspects with great patience, 
ranging from how to systematically think through complex problems 
to how to make scientific writing and presentations.
He encourages me to explore different ideas in research and is always available to give advice whenever I need it.
He is a great role model of a researcher and teacher for me to work up to.

I would also like to thank my other thesis committee members:
Prof. Andrey Korytov, Prof. Paul Avery, Prof. Konstantin Matchev, and Prof. Herman Lam.
I have learned a lot from valuable discussions with them.

I cannot express enough appreciation to Dr. Andrew Brinkerhoff and Dr. Pierluigi Bortignon,
who have mentored me as postdocs in the group.
I acquired much of my knowledge and experience from the long discussions we had and the hands-on guidance they gave.
By following their examples, I also developed my ability to perform independent researches and to handle multiple tasks.
Dr. Efe Yigitbasi joined the group later as a postdoc and helped me a lot in various research projects.
He also provided detailed comments to polish this thesis, with his amazing knowledge in theoretical physics and scientific writing.
It has been a privilege for me to work with and learn from them.
I hope to collaborate with them more in the field. 

I am lucky to have worked closely with other researchers out of the group.
Dr. Andrea Marini and Dr. Raffaele Gerosa are great examples of talented and hardworking scientists for me to follow.
Dr. Oliver Rieger, how has recently received his Ph.D., is a meticulous researcher and a reliable friend. 

I would like to thank my fellow group members who joined this field about the same time as myself:
Bhargav Joshi, Kun Shi, and Jake Rosenzweig.
It has been great to have their company so I did not feel lost as a rookie, especially when I first came to CERN. 

I spent the first three years of my Ph.D. at UF, Gainesville, and the rest three years at CERN, Geneva.
I really appreciate all the friends I have met at both places, 
who have made it so much easier to settle on a different continent and have brought so much fun to my life.
I believe many of them will continue to be my lifetime friends.
In particular, I want to mention those who shared with me the same aspiration in physics and provided mutual support in classes and research.
My cohort in physics department: Yefan Tao, Yue Yu, Chong Zhao, Bin Xu, Lintao Tan, Xinzhe Hu, and Dianteng Chen.
And my friends at CERN: Yongbin Fend, Zhicai Zhang, Miao Hu, Jiajing Mao, Rongkun Wang, Xiong Xiao, and Xu Wang.

With all my heart, I would like to convey my love to my parents and all my extended family members.
I am forever grateful to be in the best family in the world.
They made this world such a beautiful place, which kindled my pursuit to knowledge and truth.